stats-project

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

>>>>

```{r message=FALSE, warning=FALSE}
#Backward Selection
custom_fit = ols_step_best_subset(lm_fit_q2,)
custom_fit
```

```{r}
custom_model = custom_fit$model
ols_press(custom_model)
summary(custom_model)
confint(custom_model)
```

```{r}
ols_plot_cooksd_bar(custom_model)

custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
custom_model_outliers

ols_plot_dffits(custom_model)
ols_plot_diagnostics(custom_model)

ols_plot_resid_fit(custom_model)
ols_plot_resid_pot(custom_model)
ols_pred_rsq(custom_model)
plot(custom_fit)
```

custom_predictions = c(predict(custom_model, newdata = one_encode_test_data_q2))
custom_predictions

custom_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=custom_predictions)
custom_submission
#write_csv(custom_submission, "../kaggleData/customSelectionPredictions.csv")
```
